\chapter{Acknowledgments} Firstly, thank to my supervisor Prof John Morton for the opportunity to complete this project, for his support, his expert knowledge and for welcoming me into the quantum spin dynamics group during the 10 week project. I would like to also thank Prof Andrew Fisher for his involvement in guiding the theoretical treatment of this project, for insightful discussions and for good book recommendations. I would like to thank all present members of the quantum spin dynamics group for providing a friendly working environment in the shared laboratories.  

A special thank you is due to Gavin Dold and Pierandrea Conti for their involvement overseeing all aspects of this project. I thank Gavin for his kindness, patience, advise and willingness to answer any queries. In addition his direction to obtain to crucial simulations and for leading the re-installment of Zoidberg. I would like to thank Pierandrea for ensuring fabrication requiring the use of the machines at the Institute of Making was completed before the closure and for directing further fabrication. Also, I appreciate the long hours you accompanied me in the laboratory during the short available time to complete experimental measurements, for your willingness answer questions and enthusiasm to teach me to operate the equipment. 

Lastly, I would like to warmly thank CDT cohort 4 for their friendship and support throughout this year. The time spent sharing laughs, beer and lots of vegan food lifted the workload and dispelled any feeling of loneliness whilst living in London. I will greatly miss not seeing everyone of you every day. 


